\vfill
This is the night of the 10th of april 2015.\par
I'm at Gen\`eve, %and I've been just been kicked out from La Petite Reine because the place was closing :'D, as if I care. 
it's been 3 years trying to be a scientist, 5 learning from and working with them, all the time amused by their clear perspective. After two beers here are my deepest acknowledgements: From the begining...\par
My acknowledgement to Davide, the only person who has been cool every time I talk to him. My deepest acknowledgements to Alex, I wonder how the ILC course would be if I hadn't a person to tell my idea about how relationships are like airplains ... some take off fast and in very small tarmacs, some others need a long begining.\par
My acknowledgements to Nuria who is the most constant person in my life during the last 3 years. I hope she has got something good for her life from my way of living. My acknowledgements to Julia, the russian ... waaaaw, life feels hot and nice when you speak to her. My acknowledgement to Hector, that guy is going to have his signature in the world when CLIC-like lattices were built, I want to say that we admire Carl Sagan equally... I thought such thing would never happen. I want to acknowledge Javier, he is the person who got me into accelerators and it is the only subject I've been looking forward to do things for during the last 10 years. I want to send an special acknowledge to Marcin, the thrill of changing every day for our own sake is what moves us, I would like to have his energy to do stuff, cheers my friend. And now, Tenar the spanish girl who appeared in the moment I most enjoyed it. Tenar, my life is always happy when I hear from you. My biggest love during all these years, Claire. I don't 
know why, but that is probably the reason why my heart keeps beating when no one is around.\par
I want to thank Rogelio my director in CERN, the dynamics of his day to day is so dedicated to inspire people. Now, Philip, my director at LAL who is the person who stands for all what is right... I always admire how clear the world is for him. All people from ATF, FONT and KNU from whom I borrow so many spanners, cables, ideas, and sushi pieces.\par
%Daniel, the guy who knows everything about everything, so incredible ! And with whom would I talk about rare films and work at the same time... of course, only Andrea.\par
Finally, to all readers. Precisely today I wanted to be with Claire in the sunny afternoon, and this document kept me away from doing so. It is the moment to get right to the point, clear and neat. I know that Claire is fine, she always is... damn I love that girl.\par
All this is because of you, the reader. Time to flight ! ... write, write...\par
No, one more thing ``Let knowledge help us understanding how to treat our fellow men with more respect.'' by John P. Id\'arraga Mu\~noz.\par
Of course John, gracias mano.
\vfill
